Hockey Enforcers

### 2024-08-30 HocketEnforcersReport.Rmd
Relative paths.

newdataEP <-
  with(dat, data.frame(EP = c(TRUE, FALSE), 
                       GP.x = rep(mean(GP.x), 2),
                       Ht = rep(mean(Ht), 2),
                       Wt = rep(mean(Wt), 2),
                       DOB.Year = rep(mean(DOB.Year), 2),
                       I_forward = rep(1, 2))
                       )
plot(survfit(coxphmod_EP, newdata = newdataEP), conf.int = TRUE, lty = c(1,2))

>>>>

newdataEP <-
  with(dat, data.frame(EP = c(TRUE, FALSE), 
                       GP.x = rep(mean(GP.x), 2),
                       Ht = rep(mean(Ht), 2),
                       Wt = rep(mean(Wt), 2),
                       DOB.Year = rep(mean(DOB.Year), 2),
                       I_forward = rep(1, 2), 
                       Pos2 = "D")
                       )
plot(survfit(coxphmod_EP, newdata = newdataEP), conf.int = TRUE, lty = c(1,2))
